\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-12 notes/2loopNLSM.tex

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}. We will briefly review the perturbative construction of this theory below.

@@

It is tempting to try to match the pion 4pt 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4pt amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
Since the physical cuts are difficult to compare, ZM theory is being used here simply as a tool to eliminate generalized gauge freedom; ZM theory has the right power counting and kinematic structure in 2D to compare against.
Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \citepls{Nappi}.}
This introduces an extra degree of freedom into the problem.
Mechanically, the pion numerator is matched to ZM by first taking every possible assignment of right and left movers for the external particles and then restricting the pion numerator to 2D.
The loop momenta are restricted to 2D but left off-shell.
After performing the 2D matching, there are only 365 parameters of generalized gauge freedom.

The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
A generic term in the ZM numerator (of either basis graph) looks schematically like
\be
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8.
\ee
In other words, every term contains between 5 and 8 powers of loop momenta, as one would expect from a set of local, cubic Feynman rules.
\jm{I believe this is true but I need to check it.}
When the pion numerator is also forced to have this loop power counting, the number of generalized gauge freedom parameters reduces to 58.
The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}

>>>>

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}. We will briefly review the perturbative construction of this theory below.

@@

It is tempting to try to match the pion 4pt 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4pt amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
Since the physical cuts are difficult to compare, ZM theory is being used here simply as a tool to eliminate generalized gauge freedom; ZM theory has the right power counting and kinematic structure in 2D to compare against.
Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \cite{Nappi:1979ig}.}
This introduces an extra degree of freedom into the problem.
Mechanically, the pion numerator is matched to ZM by first taking every possible assignment of right and left movers for the external particles and then restricting the pion numerator to 2D.
The loop momenta are restricted to 2D but left off-shell.
After performing the 2D matching, there are only 365 parameters of generalized gauge freedom.

The loop momentum structure of ZM theory provides one final hint for simplifying the pion numerators.
A generic term in the ZM numerator (of either basis graph) looks schematically like
\be
\label{eq:ZMLoopPowCount}
\ell_1^m \ell_2^n k^{12-(m+n)} \text{ where } 5 \leq m+n \leq 8,
\ee
whereas a generic set of local, cubic Feynman rules could have produced terms with up to $m+n=12$ powers of loop momenta.
When the pion numerator is forced to have the loop power counting structure in \cref{eq:ZMLoopPowCount} of ZM theory, the number of generalized gauge freedom parameters reduces to 58.
The pion numerator appearing in the ancillary files contains only these 58 degrees of freedom.\footnote{When the 4pt pion amplitude is normalized to $-k_1\cdot k_2$ and the ZM vertex is normalized to $k_1^\mu \epsilon_{\mu\nu}k_2^\nu$, the parameter $z$ is fixed to $216/565$, which is clearly unrelated to the difference in coupling constants.}
